Another paper with lots of text and fancy pictures

### 2023-11-27 paper.tex
Add heatmaps of S₃ for highly anisotropic samples

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Note
that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
samples are on \cref{fig:samples}. On plots of correlation functions we provide
a family of curves with the first argument of the correlation function being
fixed.

@@

Correlation functions for the SEM sample are on
\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
diameter.
\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

\begin{figure*}[tp]
  \centering
  \subfigure[Limestone]{
    \includegraphics[width=0.45\linewidth]{images/carb.png}
    \label{fig:sample-limestone}}
  \hfill
  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

>>>>

\section{Results}
In this section we compute correlation functions along the plane $XY$ for 2- and
3-dimensional real samples. Table \ref{tab:summary} contains information about
these samples. Note that we compute surface correlation functions only for those
samples for which the criterion $C_{0.5} > 0.97$ holds. Images of the samples
are on \cref{fig:samples}. On plots of correlation functions we provide a family
of curves with the first argument of the correlation function being fixed. For
two highly anisotropic samples (the soil and the shale) we provide heatmaps of
$S_3$ correlation function where anisotropicity can be easily seen. These two
samples was preliminary rotated by $\frac{\pi}{4}$ around the axis $Z$ before
calculation of correlation functions.

@@

Correlation functions for the SEM sample are on
\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
diameter.

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}.

\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Soil & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

\begin{figure*}[tp]
  \centering
  \subfigure[Limestone]{
    \includegraphics[width=0.45\linewidth]{images/carb.png}
    \label{fig:sample-limestone}}
  \hfill
  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible.}
  \label{fig:heatmaps}
\end{figure*}
